---
title: "MA_analyses_per_feature"
author: "David Quiroga"
date: "02-07/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

set relevant libraries:
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ez)
library(knitr)
```

Load and organize data:
```{r}
# load data:
data = read.csv('../../data/MA/MA.csv',header = TRUE)

# rename conditions:
data$condition <- as.character(data$condition)
data[which(data$condition == 'optimal'),'condition'] <- 'LC'
data[which(data$condition == 'alberti'),'condition'] <- 'IC'
data[which(data$condition == 'melody'),'condition'] <- 'HC'

# fix factor order:
data$condition = factor(data$condition, levels =c('LC','IC','HC','familiar','unfamiliar','hihat'))
data$feature = factor(data$feature, levels = c('pitch','intensity','timbre', 'location','rhythm'))
data$group = factor(data$group, levels = c('controls','amusics'))

data$amplitude = data$amplitude/10^-06 # convert to micro Volts
data <- data[!grepl('rhythm',data$feature),] # exclude rhtyhm MMN
```

select complexity data:
```{r}
cdata <- data[grepl('LC',data$condition) |
             grepl('IC',data$condition) |
             grepl('HC',data$condition),]
```

show sphericity corrections?

```{r}
detailed = FALSE # change to TRUE to show corrections
```

Perform complexity tests on mean amplitudes for all features:
```{r}
for (f in unique(cdata$feature)){
  catest <- ezANOVA(data= cdata[which(cdata$feature == f),],
                   amplitude,subject,within = c(condition),
                   between = c(group),detailed = detailed)
  print(kable(catest$ANOVA, caption = paste0('ANOVA results ','(', f, ')')))

  if (detailed){
    print( kable(catest$`Mauchly's Test for Sphericity`, caption = 'sphericity tests'))
    print( kable(catest$`Sphericity Corrections`, caption = 'sphericity corrections:'))
  }
  cat("\n")
}
```

Perform complexity tests on peak latencies for all features:
```{r}
for (f in unique(cdata$feature)){
  cltest <- ezANOVA(data= cdata[which(cdata$feature == f),],
                   latency,subject,within = c(condition),
                   between = c(group),detailed = detailed)
  print(kable(cltest$ANOVA, caption = paste0('ANOVA results ','(', f, ')')))

  if (detailed){
    print( kable(cltest$`Mauchly's Test for Sphericity`, caption = 'sphericity tests'))
    print( kable(cltest$`Sphericity Corrections`, caption = 'sphericity corrections:'))
  }
  cat("\n")
}
```

select familiarity data:
```{r}
fdata <- data[grepl('familiar',data$condition) |
              grepl('unfamiliar',data$condition),]
```

Perform familiarity tests on mean amplitudes for all features:
```{r}
for (f in unique(fdata$feature)){
  fatest <- ezANOVA(data= fdata[which(fdata$feature == f),],
                   amplitude,subject,within = c(condition),
                   between = c(group),detailed = detailed)
  print(kable(fatest$ANOVA, caption = paste0('ANOVA results ','(', f, ')')))

  if (detailed){
    print( kable(fatest$`Mauchly's Test for Sphericity`, caption = 'sphericity tests'))
    print( kable(fatest$`Sphericity Corrections`, caption = 'sphericity corrections:'))
  }
  cat("\n")
}
```

Perform familiarity tests on peak latencies for all features:
```{r}
for (f in unique(fdata$feature)){
  fltest <- ezANOVA(data= fdata[which(fdata$feature == f),],
                   latency,subject,within = c(condition),
                   between = c(group),detailed = detailed)
  print(kable(fltest$ANOVA, caption = paste0('ANOVA results ','(', f, ')')))

  if (detailed){
    print( kable(fltest$`Mauchly's Test for Sphericity`, caption = 'sphericity tests'))
    print( kable(fltest$`Sphericity Corrections`, caption = 'sphericity corrections:'))
  }
  cat("\n")
}
```