---
title: "Mean amplitude analyses"
author: "David Quiroga"
date: "02/07-2020"
output: html_document# pdf_document#
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

set relevant libraries:
```{r message=FALSE, warning=FALSE}
library(lme4)
library(ggplot2)
library(ez)
library(emmeans)
library(gridExtra)
library(knitr)

```

load and organize data:

```{r}
#data = read.csv('../../data/MA_grand_window.csv',header = TRUE)
data = read.csv('../../data/MA/MA.csv',header = TRUE, dec = ",")

# rename conditions:
data$condition <- as.character(data$condition)
data[which(data$condition == 'optimal'),'condition'] <- 'LC'
data[which(data$condition == 'alberti'),'condition'] <- 'IC'
data[which(data$condition == 'melody'),'condition'] <- 'HC'

# order factors:
data$condition = factor(data$condition,
                        levels = c('LC','IC','HC',
                                   'familiar','unfamiliar','hihat'))
data$feature = factor(data$feature,
                      levels = c('pitch','intensity','timbre',
                                 'location','rhythm'))
data$group = factor(data$group,
                    levels = c('controls','amusics'))

data$amplitude <- as.numeric(as.character(data$amplitude))
data$latency <- as.numeric(as.character(data$latency))

data$amplitude = data$amplitude/10^-06 # convert to micro Volts

data <- data[!grepl('rhythm',data$feature),] # exclude rhythm
```

Now let's perform complexity analyses:

First, select data:

```{r}
cdata <- data[grepl('LC',data$condition) |
             grepl('IC',data$condition) |
             grepl('HC',data$condition),]
```

COMPLEXITY ANALYSES - amplitude 

Fit mixed-effects models:
```{r}

m0 <- lmer(amplitude~1 + (1|subject),data = cdata);#summary(m0)
m1 <- lmer(amplitude~condition + (1|subject), data = cdata);#summary(m1)
m2 <- lmer(amplitude~condition + group + (1|subject), data = cdata);#summary(m2)
m3 <- lmer(amplitude~condition + group + feature + (1|subject),
           data = cdata);#summary(m3)
m4 <- lmer(amplitude~condition + group + feature + condition:feature + (1|subject),
           data = cdata);#summary(m4)
m5 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group + (1|subject),
           data = cdata);#summary(m5)
m6 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + (1|subject),
           data = cdata);#summary(m6)
m7 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + condition:group:feature + (1|subject),
           data = cdata);#summary(m7)
```

Now perform Likelihood ratio test and store models:

```{r}
camp.test <- anova(m0,m1,m2,m3,m4,m5,m6,m7);camp.test # Likelihood ratio test
camp.models <- list(m0,m1,m2,m3,m4,m5,m6,m7) # store models for report
```


Models 1, 3 and 4 are significant, indicating effects of feature, condition and a feature:condition interaction

Let's try to reproduce the results with ANOVA:

```{r}
caov <- ezANOVA(data= cdata, amplitude,subject,within = c(condition,feature),
        between = c(group),detailed = TRUE)
kable(caov$ANOVA)

```


Results are the same!

Now let's do some pairwise contrasts:

```{r}
confint.camp <- as.data.frame(confint(lsmeans(m4,pairwise~condition|feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.camp <-cbind(as.data.frame(lsmeans(m4, pairwise~condition|feature,
                                            adjust="bonferroni")$contrasts),
                      confint.camp[c("lower.CL","upper.CL")])
pairwise.camp <- pairwise.camp[c("feature","contrast","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.camp[,"d"] <- pairwise.camp$estimate/sqrt(VarCorr(m4)$subject[1] + sigma(m4)^2)
pairwise.camp[,3:8] <- round(pairwise.camp[,3:8],2)
colnames(pairwise.camp) <- c("feature","contrast","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")

kable(pairwise.camp)
write.table(pairwise.camp,file="../results/pairwise_camp.csv",
            sep=",",row.names = FALSE,quote=FALSE) # Export to a table
```


And now a plot:

```{r}
camp <- ggplot(cdata,aes(condition, amplitude)) +
  geom_hline(yintercept = 0) +
  geom_point(alpha = 0.6,color = 'black',size = 0.8) +
  geom_line(aes(group = subject), alpha = 0.15) +
  geom_boxplot(aes(fill = group),alpha = 0.3,
               color = 'black', width = 0.2) +
  geom_violin(aes(color = group),color = 'black',
              alpha = 0.2,trim = FALSE) + 
  scale_fill_manual(values = c('blue','red')) +
  facet_grid(feature~group) +
  xlab('complexity') +
  ylab('mean amplitude (\U1D707V)') +
  scale_x_discrete(labels=c("low", "int.","high",
                            "low", "int.","high")) +
  theme_bw() +
  theme(legend.position = "none"); camp
```

COMPLEXITY ANALYSES - Latency

Fit mixed effects models:

```{r}

latm0 <- lmer(latency~1 + (1|subject),data = cdata);#summary(latm0)
latm1 <- lmer(latency~condition + (1|subject), data = cdata);#summary(latm1)
latm2 <- lmer(latency~condition + group + (1|subject), data = cdata);#summary(latm2)
latm3 <- lmer(latency~condition + group + feature + (1|subject),
              data = cdata);#summary(latm3)
latm4 <- lmer(latency~condition + group + feature + condition:feature + (1|subject),
              data = cdata);#summary(latm4)
latm5 <- lmer(latency~condition + group + feature + 
                condition:feature + condition:group + (1|subject),
              data = cdata);#summary(latm5)
latm6 <- lmer(latency~condition + group + feature + 
                condition:feature + condition:group +
                group:feature + (1|subject),
              data = cdata);#summary(latm6)
latm7 <- lmer(latency~condition + group + feature + 
                condition:feature + condition:group +
                group:feature + condition:group:feature + (1|subject),
                data = cdata) #; summary(latm7)

```

Likelihood ratio test and store models:

```{r}
clat.test <- anova(latm0,latm1,latm2,latm3,latm4,latm5,latm6,latm7); clat.test
clat.models <- list(latm0,latm1,latm2,latm3,latm4,latm5,latm6,latm7)
```


Same results as for mean amplitudes, although now there is evidence for a group:feature interaction, meaning amusics had longer latencies than controls for pitch MMN across conditions (see below). However, note the high p-value and the fact that the winning model in terms of AIC was latm3. In sum, evidence not entirely conclusive.

Now let's confirm this with an ANOVA:
```{r}
claov <- ezANOVA(data = cdata, latency,subject,within = c(condition,feature),
         between = c(group),detailed = TRUE)
kable(claov$ANOVA)

```


The results are the same, but note that the interaction group:feature is not detected anymore. There was a trend, though.

Now let's do pairwise comparisons:

```{r}
confint.clat <- as.data.frame(confint(lsmeans(latm4,pairwise~condition|feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.clat <-cbind(as.data.frame(lsmeans(latm4, pairwise~condition|feature,
                                            adjust="bonferroni")$contrasts),
                      confint.clat[c("lower.CL","upper.CL")])
pairwise.clat <- pairwise.clat[c("feature","contrast","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.clat[," d"] <- pairwise.clat$estimate/sqrt(VarCorr(latm4)$subject[1] + sigma(latm4)^2)
pairwise.clat[,3:8] <- round(pairwise.clat[,3:8],2)
colnames(pairwise.clat) <- c("feature","contrast","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.clat)
write.table(pairwise.clat,file="../results/pairwise_clat1.csv",
            sep=",",row.names = FALSE,quote=FALSE) # Export to a table
```

Now pairwise contrasts: group:feature

```{r}
confint.clat2 <- as.data.frame(confint(lsmeans(latm6,pairwise~group|feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.clat2 <-cbind(as.data.frame(lsmeans(latm6, pairwise~group|feature,
                                            adjust="bonferroni")$contrasts),
                      confint.clat2[c("lower.CL","upper.CL")])
pairwise.clat2 <- pairwise.clat2[c("feature","contrast","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.clat2[,"d"] <- pairwise.clat2$estimate/sqrt(VarCorr(latm6)$subject[1] + sigma(latm6)^2)
pairwise.clat2[,3:8] <- round(pairwise.clat2[,3:8],2)
colnames(pairwise.clat2) <- c("feature","contrast","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.clat2)
write.table(pairwise.clat2,file="../results/pairwise_clat2.csv",
            sep=",",row.names = FALSE,quote=FALSE)
```


Here it can be seen that amusics had longer MMN latencies than controls for pitch (20 ms difference)

Now a plot:

```{r}
clat <- ggplot(cdata,aes(condition, latency)) +
  geom_hline(yintercept = 0) +
  geom_point(alpha = 0.6,color = 'black',size = 0.8) +
  geom_line(aes(group = subject), alpha = 0.15) +
  geom_boxplot(aes(fill = group),alpha = 0.3,
               color = 'black', width = 0.2) +
  geom_violin(aes(color = group),color = 'black',
              alpha = 0.2,trim = FALSE) + 
  scale_fill_manual(values = c('blue','red')) +
  facet_grid(feature~group) +
  xlab('complexity') +
  ylab('peak latency (ms)') +
  scale_x_discrete(labels=c("low", "int.","high",
                            "low", "int.","high")) +
  theme_bw() +
  theme(legend.position = "none");clat
```

Now let's make a joint report for complexity effects regarding latency and amplitude:
```{R}
complexity.report <- data.frame('model' = rownames(camp.test))
complexity.report[2:nrow(complexity.report),'null'] <- complexity.report[1:nrow(complexity.report)-1,'model']
                            
complexity.report <- cbind(complexity.report,round(camp.test[,c('AIC','Chisq','Pr(>Chisq)')],2),
                                 round(clat.test[,c('AIC','Chisq','Pr(>Chisq)')],2))
colnames(complexity.report) <- c('model','null','AIC','X2','p','AIC','X2','p')

write.table(complexity.report,file="../results/complexity.report.csv",
            sep= ",",row.names = FALSE,quote=FALSE)
kable(complexity.report)
```

And a similar pairwise table:
```{r}
complexity.pw <- cbind(pairwise.camp,pairwise.clat[,c(3:ncol(pairwise.clat))])
write.table(complexity.pw,file="../results/pairwise_complexity.csv",
            sep=",",row.names = FALSE,quote=FALSE)
kable(complexity.pw)
```

And let's put the complexity plots together:
```{r}
cplots <- arrangeGrob(camp,clat,ncol=2);plot(cplots)
ggsave("../results/MA_complexity.pdf", plot=cplots,width = 170, height = 150, units = 'mm', dpi = 300)
ggsave("../results/MA_complexity.png", plot=cplots,width = 170, height = 150, units = 'mm', dpi = 300)
```

Now let's move on to familiarity analyses - first, select data:

```{r}
fdata = data[grepl('familiar',data$condition) |
             grepl('unfamiliar',data$condition),]
```

FAMILIARITY ANALYSES - Amplitudes

fit mixed-effects models:
```{r}
fm0 <- lmer(amplitude~1 + (1|subject),data = fdata)#;summary(fm0)
fm1 <- lmer(amplitude~condition + (1|subject), data = fdata)#;summary(fm1)
fm2 <- lmer(amplitude~condition + group + (1|subject), data = fdata)#;summary(fm2)
fm3 <- lmer(amplitude~condition + group + feature + (1|subject),
           data = fdata)#;summary(fm3)
fm4 <- lmer(amplitude~condition + group + feature + condition:feature + (1|subject),
           data = fdata)#;summary(fm4)
fm5 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group + (1|subject),
           data = fdata)#;summary(fm5)
fm6 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + (1|subject),
           data = fdata)#;summary(fm6)
fm7 <- lmer(amplitude~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + condition:group:feature + (1|subject),
           data = fdata)#;summary(fm7)
```

Likelihood ratio test and store models:

```{r}
famp.test <- anova(fm0,fm1,fm2,fm3,fm4,fm5,fm6,fm7); famp.test
famp.models <- list(fm0,fm1,fm2,fm3,fm4,fm5,fm6,fm7)
```

The results clearly show an effect of feature but nothing else

Let's confirm with ANOVA:

```{r}
faov <- ezANOVA(data= fdata, amplitude,subject,within = c(condition,feature),
        between = c(group),detailed = TRUE)
kable(faov$ANOVA)
```


The anova suggested also a feature by condition interaction, which was only a trend in the LR test. Otherwise, results are identical

Let's do some pairwise contrasts:
```{r}
confint.famp <- as.data.frame(confint(lsmeans(fm4,pairwise~feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.famp <-cbind(as.data.frame(lsmeans(fm4, pairwise~feature,
                                            adjust="bonferroni")$contrasts),
                      confint.famp[c("lower.CL","upper.CL")])
pairwise.famp <- pairwise.famp[c("contrast","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.famp[,"d"] <- pairwise.famp$estimate/sqrt(VarCorr(fm4)$subject[1] + sigma(fm4)^2)
pairwise.famp[,2:7] <- round(pairwise.famp[,2:7],2)
colnames(pairwise.famp) <- c("contrast","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.famp)

write.table(pairwise.famp,file="../results/pairwise_famp1.csv",
            sep=",",row.names = FALSE,quote=FALSE) # Export to a table


```

And now taking into account the conditions:
```{r}
confint.famp2 <- as.data.frame(confint(lsmeans(fm4,pairwise~condition|feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.famp2 <-cbind(as.data.frame(lsmeans(fm4, pairwise~condition|feature,
                                            adjust="bonferroni")$contrasts),
                      confint.famp2[c("lower.CL","upper.CL")])
pairwise.famp2 <- pairwise.famp2[c("contrast","feature","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.famp2[,"d"] <- pairwise.famp2$estimate/sqrt(VarCorr(fm4)$subject[1] + sigma(fm4)^2)
pairwise.famp2[,3:8] <- round(pairwise.famp2[,3:8],2)
colnames(pairwise.famp2) <- c("contrast","feature","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.famp2)

write.table(pairwise.famp2,file="../results/pairwise_famp2.csv",
            sep=",",row.names = FALSE,quote=FALSE)

```

This confirms the differences for intensity

And now taking into account the conditions per group:

```{r}
confint.famp3 <- as.data.frame(confint(lsmeans(fm7,pairwise~condition|group|feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.famp3 <-cbind(as.data.frame(lsmeans(fm7, pairwise~condition|group|feature,
                                            adjust="bonferroni")$contrasts),
                      confint.famp3[c("lower.CL","upper.CL")])
pairwise.famp3 <- pairwise.famp3[c("contrast","feature","group","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.famp3[,"d"] <- pairwise.famp3$estimate/sqrt(VarCorr(fm7)$subject[1] + sigma(fm7)^2)
pairwise.famp3[,4:9] <- round(pairwise.famp3[,4:9],2)
colnames(pairwise.famp3) <- c("contrast","feature","group","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.famp3)

write.table(pairwise.famp3,file="../results/pairwise_famp3.csv",
            sep=",",row.names = FALSE,quote=FALSE)
ref <- VarCorr(fm7)
```


Now let's make a figure:
```{r}
famp <- ggplot(fdata,aes(condition, amplitude)) +
  geom_hline(yintercept = 0) +
  geom_point(alpha = 0.6,color = 'black',size = 0.8) +
  geom_line(aes(group = subject), alpha = 0.15) +
  geom_boxplot(aes(fill = group),alpha = 0.3,
               color = 'black', width = 0.2) +
  geom_violin(aes(color = group),color = 'black',
              alpha = 0.2,trim = FALSE) + 
  scale_fill_manual(values = c('blue','red')) +
  facet_grid(feature~group) +
  xlab('familiarity') +
  ylab('mean amplitude (\U1D707V)') +
  theme_bw() +
  theme(legend.position = "none"); famp

```

FAMILIARITY ANALYSES - latencies

fitting mixed-effects models:
```{r}

flatm0 <- lmer(latency~1 + (1|subject),data = fdata)#;summary(flatm0)
flatm1 <- lmer(latency~condition + (1|subject), data = fdata)#;summary(flatm1)
flatm2 <- lmer(latency~condition + group + (1|subject), data = fdata)#;summary(flatm2)
flatm3 <- lmer(latency~condition + group + feature + (1|subject),
           data = fdata)#;summary(flatm3)
flatm4 <- lmer(latency~condition + group + feature + condition:feature + (1|subject),
           data = fdata)#;summary(flatm4)
flatm5 <- lmer(latency~condition + group + feature + 
             condition:feature + condition:group + (1|subject),
           data = fdata)#;summary(flatm5)
flatm6 <- lmer(latency~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + (1|subject),
           data = fdata)#;summary(flatm6)
flatm7 <- lmer(latency~condition + group + feature + 
             condition:feature + condition:group +
             group:feature + condition:group:feature + (1|subject),
           data = fdata)#;summary(flatm7)

```


Likelihood ratio test and store models:

```{r}
flat.test <- anova(flatm0,flatm1,flatm2,flatm3,flatm4,flatm5,flatm6,flatm7); flat.test
flat.models <- list(flatm0,flatm1,flatm2,flatm3,flatm4,flatm5,flatm6,flatm7)
```

an effect of feature but nothing else

Let's confirm with an ANOVA:

```{r}
flaov <- ezANOVA(data= fdata, latency,subject,within = c(condition,feature),
         between = c(group),detailed = TRUE)
kable(flaov$ANOVA)
```

Same results!

Now let's do pairwise comparisons:

```{r}
confint.flat <- as.data.frame(confint(lsmeans(flatm4,pairwise~feature,
                                              adjust = "Bonferroni")$contrast))
pairwise.flat <-cbind(as.data.frame(lsmeans(flatm4, pairwise~feature,
                                            adjust="bonferroni")$contrasts),
                      confint.flat[c("lower.CL","upper.CL")])
pairwise.flat <- pairwise.flat[c("contrast","estimate","lower.CL",
                                 "upper.CL","t.ratio","p.value")]
pairwise.flat[,"d"] <- pairwise.flat$estimate/sqrt(VarCorr(flatm4)$subject[1] + sigma(flatm4)^2)
pairwise.flat[,2:7] <- round(pairwise.flat[,2:7],2)
colnames(pairwise.flat) <- c("contrast","estimate",
                             "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.flat)

write.table(pairwise.flat,file="../results/pairwise_flat1.csv",
            sep=",",row.names = FALSE,quote=FALSE) # Export to a table
```

Another perspective:

```{r}
confint.flat2 <- as.data.frame(confint(lsmeans(flatm4,pairwise~condition|feature,
                                               adjust = "Bonferroni")$contrast))
pairwise.flat2 <-cbind(as.data.frame(lsmeans(flatm4, pairwise~condition|feature,
                                             adjust="bonferroni")$contrasts),
                       confint.flat2[c("lower.CL","upper.CL")])
pairwise.flat2 <- pairwise.flat2[c("contrast","feature","estimate","lower.CL",
                                   "upper.CL","t.ratio","p.value")]
pairwise.flat2[,"d"] <- pairwise.flat2$estimate/sqrt(VarCorr(flatm4)$subject[1] + sigma(flatm4)^2)
pairwise.flat2[,3:8] <- round(pairwise.flat2[,3:8],2)
colnames(pairwise.flat2) <- c("contrast","feature","estimate",
                              "CI 2.5%","CI 97.5%","t","p","d")
kable(pairwise.flat2)

write.table(pairwise.flat2,file="../results/pairwise_flat2.csv",
            sep=",",row.names = FALSE,quote=FALSE)
```

Make a figure
```{r}
flat <- ggplot(fdata,aes(condition, latency)) +
  geom_hline(yintercept = 0) +
  geom_point(alpha = 0.6,color = 'black', size = 0.6) +
  geom_line(aes(group = subject), alpha = 0.15) +
  geom_boxplot(aes(fill = group),alpha = 0.3,
               color = 'black', width = 0.2) +
  geom_violin(aes(color = group),color = 'black',
              alpha = 0.2,trim = FALSE) + 
  scale_fill_manual(values = c('blue','red')) +
  facet_grid(feature~group) +
  xlab('familiarity') +
  ylab('peak latency (ms)') +
  theme_bw() +
  theme(legend.position = "none"); flat

```

Make joint familiarity reports:

```{r}

familiarity.report <- data.frame('model' = rownames(famp.test))
familiarity.report[2:nrow(familiarity.report),'null'] <- familiarity.report[1:nrow(familiarity.report)-1,'model']

familiarity.report <- cbind(familiarity.report,round(famp.test[,c('AIC','Chisq','Pr(>Chisq)')],2),
                           round(flat.test[,c('AIC','Chisq','Pr(>Chisq)')],2))
colnames(familiarity.report) <- c('model','null','AIC','X2','p','AIC','X2','p')

write.table(familiarity.report,file="../results/familiarity.report.csv",
            sep= ",",row.names = FALSE,quote=FALSE)
kable(familiarity.report)
```

```{r}
familiarity.pw <- cbind(pairwise.famp,pairwise.flat[,c(2:ncol(pairwise.flat))])
write.table(familiarity.pw,file="../results/pairwise_familiarity.csv",
            sep=",",row.names = FALSE,quote=FALSE)
kable(familiarity.pw)
```

And make a joint figure:

```{r}
fplots <- arrangeGrob(famp,flat,ncol=2);plot(fplots)
ggsave("../results/MA_familiarity.pdf", plot=fplots,width = 170, height = 150, units = 'mm', dpi = 300)
ggsave("../results/MA_familiarity.png", plot=fplots,width = 170, height = 150, units = 'mm', dpi = 300)

```

Finally, let's do some exploratory correlation analyses of MBEA and MMN amplitudes
```{r}
cors <- data.frame()
ct <- 0
for (c in unique(data$condition)){
  for (f in unique(data$feature)){
    ct = ct+1
    curd <-data[data$feature == f & data$condition == c, ] 
    cor_MBEA <- cor.test(curd$MBEA,curd$amplitude)
    cor_MBEA_p <- cor.test(curd$MBEA_pitch,curd$amplitude)
    cors[ct,'condition'] <- c
    cors[ct,'feature'] <- f
    cors[ct,'r(MBEA)'] <- cor_MBEA$estimate
    cors[ct,'p(MBEA)'] <- cor_MBEA$p.value
    cors[ct,'r(MBEA.pitch)'] <- cor_MBEA_p$estimate
    cors[ct,'p(MBEA.pitch)'] <- cor_MBEA_p$p.value
  }
}
cors[,3:6] <- round(cors[,3:6],2)
kable(cors)
```
And latencies:
```{r}
corsl <- data.frame()
ct <- 0
for (c in unique(data$condition)){
  for (f in unique(data$feature)){
    ct = ct+1
    curd <-data[data$feature == f & data$condition == c, ] 
    cor_MBEA <- cor.test(curd$MBEA,curd$latency)
    cor_MBEA_p <- cor.test(curd$MBEA_pitch,curd$latency)
    corsl[ct,'condition'] <- c
    corsl[ct,'feature'] <- f
    corsl[ct,'r(MBEA)'] <- cor_MBEA$estimate
    corsl[ct,'p(MBEA)'] <- cor_MBEA$p.value
    corsl[ct,'r(MBEA.pitch)'] <- cor_MBEA_p$estimate
    corsl[ct,'p(MBEA.pitch)'] <- cor_MBEA_p$p.value
  }
}
corsl[,3:6] <- round(corsl[,3:6],2)
kable(corsl)
```
