---
title: "Mean amplitude analyses - Bayesian"
author: "David Quiroga"
date: "02/07-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

set relevant libraries:
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ez)
library(knitr)
library(brms)
```

Load and organize data:
```{r}
# load data:
data = read.csv('../../data/MA/MA.csv',header = TRUE)

# rename conditions:
data$condition <- as.character(data$condition)
data[which(data$condition == 'optimal'),'condition'] <- 'LC'
data[which(data$condition == 'alberti'),'condition'] <- 'IC'
data[which(data$condition == 'melody'),'condition'] <- 'HC'

# fix factor order:
data$condition = factor(data$condition, levels =c('LC','IC','HC','familiar','unfamiliar','hihat'))
data$feature = factor(data$feature, levels = c('pitch','intensity','timbre', 'location','rhythm'))
data$group = factor(data$group, levels = c('controls','amusics'))

data$amplitude = data$amplitude/10^-06 # convert to micro Volts
data <- data[!grepl('rhythm',data$feature),] # exclude rhtyhm MMN
```

select complexity data and pitch:
```{r}
cdata <- data[(grepl('LC',data$condition) |
             grepl('IC',data$condition) |
             grepl('HC',data$condition)) & 
             grepl('pitch',data$feature),]
```

Inspect prior structure:

```{r}
prior_prelim = get_prior(amplitude~group*condition + (1|subject), data = cdata)

```

define a conservative prior for the interaction centered around 0:
```{r}
 priors1 <-  c(set_prior('normal(0,1)', coef = 'groupamusics:conditionIC'),
               set_prior('normal(0,1)', coef = 'groupamusics:conditionHC'))
```

define a less conservative prior for the interaction centered around 1 microvolt:
```{r}
 priors2 <-  c(set_prior('normal(1,1)', coef = 'groupamusics:conditionIC'),
               set_prior('normal(1,1)', coef = 'groupamusics:conditionHC'))
```

Fit models to data:
```{r}
b0 <- brm(amplitude~0 + intercept +
            group + condition +
            (1|subject),
            data = cdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            seed = 050990,
            iter = 1000)

b1 <- brm(amplitude~0 + intercept +
            group*condition +
            (1|subject),
            data = cdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            prior = priors1,
            seed = 050990,
            iter = 1000)

b2 <- brm(amplitude~0 + intercept +
            group*condition +
            (1|subject),
            data = cdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            prior = priors2,
            seed = 050990,
            iter = 1000)

```

obtain Bayes factors for the interaction terms:
```{r}
hypotheses <- c('groupamusics:conditionIC = 0',
                'groupamusics:conditionHC = 0')
BF.b1 <- hypothesis(b1,hypotheses);BF.b1
BF.b2 <- hypothesis(b2,hypotheses);BF.b2

```

The results indicate that Bayes factors remain between 0.35 and 1.47 which constitutes pretty inconclusive evidence for an interaction between group and condition

We can also compare models against the null directly:
```{r}
bayes_factor(b0,b1)
bayes_factor(b0,b2)

```

in both cases the Bayes factors favor a null model, but their are still very inconlusive


Now we do the same analyses for familiarity analyses

First, select data:
```{r}
fdata <- data[(grepl('familiar',data$condition) |
             grepl('unfamiliar',data$condition)) & 
             grepl('pitch',data$feature),]
```


Inspect prior structure:

```{r}
fprior_prelim = get_prior(amplitude~group*condition + (1|subject), data = fdata)

```

define a conservative prior for the interaction centered around 0:
```{r}
 fpriors1 <-  c(set_prior('normal(0,1)', coef = 'groupamusics:conditionunfamiliar'))
```

define a less conservative prior for the interaction centered around 1 microvolt:
```{r}
 fpriors2 <-  c(set_prior('normal(1,1)', coef = 'groupamusics:conditionunfamiliar'))
```

Fit models to data:
```{r}
f0 <- brm(amplitude~0 + intercept +
            group + condition +
            (1|subject),
            data = fdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            seed = 050990,
            iter = 1000)

f1 <- brm(amplitude~0 + intercept +
            group*condition +
            (1|subject),
            data = fdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            prior = fpriors1,
            seed = 050990,
            iter = 1000)

f2 <- brm(amplitude~0 + intercept +
            group*condition +
            (1|subject),
            data = fdata,
            cores=8,
            sample_prior = TRUE,
            save_all_pars = TRUE,
            prior = fpriors2,
            seed = 050990,
            iter = 1000)

```


obtain Bayes factors for the interaction term:
```{r}
hypotheses <- c('groupamusics:conditionunfamiliar = 0')
BF.f1 <- hypothesis(f1,hypotheses);BF.f1
BF.f2 <- hypothesis(f2,hypotheses);BF.f2

```

Bayes factors are 0.56 and 0.5, still very inconclusive.

We can also compare models against the null directly:
```{r}
bayes_factor(f0,f1)
bayes_factor(f0,f2)

```

We confirm the inconclusiveness of BF: 0.48 and 0.65


Finally let's plot the models to check convergence:
```{r}
plot(b1, ask = FALSE)
```

```{r}
plot(b2, ask = FALSE)
```

```{r}
plot(f1, ask = FALSE)
```

```{r}
plot(f2, ask = FALSE)
```